Prediction of the 2020 Presidential Elections

### 2020-10-25 outputs/paper/paper.Rmd
Added the reference for the ACS and nationscape data. changed the directory for the scripts and included our info

---
title: "Prediction of the 2020 Presidential Elections"
subtitle: "Spoiler alert: Biden Wins"
author: "Anees Shaikh, Jaffa Romain, and Lu Mu"
thanks: "Code and data are available at: https://github.com/aneesshake/elections_prediction"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: |
  | First sentence. Second sentence. Third sentence. Fourth sentence.
  |
  | **Keywords:** forecasting; US 2020 election; Trump;Biden
output:
  bookdown::pdf_document2:
    citation_package: natbib
toc: FALSE
bibliography: references.bib
---

@@

>>>>

---
title: "Prediction of the 2020 Presidential Elections"
subtitle: "Spoiler alert: Biden Wins"
author: "Anees Shaikh, Jaffa Romain, and Lu Mu"
thanks: "Code and data are available at: https://github.com/aneesshake/elections_prediction"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: |
  | First sentence. Second sentence. Third sentence. Fourth sentence.
  |
  | **Keywords:** forecasting; US 2020 election; Trump; Biden
output:
  bookdown::pdf_document2:
    citation_package: natbib
toc: FALSE
bibliography: references.bib
---

@@

Tausanovitch, Chris and Lynn Vavreck. 2020. Democracy Fund + UCLA Nationscape, October 10-17, 2019 (version 20200814). Retrieved from [URL].

Steven Ruggles, Sarah Flood, Ronald Goeken, Josiah Grover, Erin Meyer, Jose Pacas and Matthew Sobek. IPUMS USA: Version 10.0 [dataset]. Minneapolis, MN: IPUMS, 2020. https://doi.org/10.18128/D010.V10.0
